Financial_Analysis

### 2016-06-17 financial.rmd
reviewed lit review started method review

profit <- function(df = all10mice, method = c("average","simp.log","orig.log","orig.rf","orig.boost"), 
                   seed = 300, 
                   k.folds = 5, # number of folds in initial model.blend generation
                   max.iter = 5, #max number of iterations from initial model.blend generation
                   k.folds.2 = 5, # number of folds for second step blended model development
                   tot.tests = 50 # total number of results to create
                   ){

@@

@@

@@

# saveRDS(plot.results,"C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/plot_finance.rds" )

>>>>

profit <- function(df = all10mice, method = c("average","simp.log","orig.log","orig.rf","orig.boost"), 
                   seed = 300, 
                   k.folds = 5, # number of folds in initial model.blend generation
                   max.iter = 5, #max number of iterations from initial model.blend generation
                   k.folds.2 = 5, # number of folds for second step blended model development
                   tot.tests = 500 # total number of results to create
                   ){

@@

        assign("prof.results", prof.results, envir = .GlobalEnv)

@@

#function below assigns results to 'prof.results' object in global env
# profit(df = all10mice, method = c("average","simp.log","orig.log","orig.rf","orig.boost"), 
#                    seed = 300, 
#                    k.folds = 5, # number of folds in initial model.blend generation
#                    max.iter = 5, #max number of iterations from initial model.blend generation
#                    k.folds.2 = 5, # number of folds for second step blended model development
#                    tot.tests = 500 # total number of results to create
#                    )

@@

# saveRDS(plot.results,"C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/plot_finance_100.rds" )
